---
title: "Homework 3"
author: "Justin Li"
date: "2022-10-16"
output: html_document
---

https://github.com/Lord-Bubbles/Stat-433-Homework-3

```{r setup, include=FALSE}
library(nycflights13)
library(dplyr)
library(ggplot2)
knitr::opts_chunk$set(echo = TRUE)
```

## Questions from 13.4.6

1. Compute the average delay by destination, then join on the airports data 
frame so you can show the spatial distribution of delays.
```{r, warning = FALSE}
flights %>%
  group_by(dest) %>%
  summarise(avg_delay = mean(arr_delay, na.rm = T)) %>%
  left_join(airports, c("dest" = "faa")) %>%
  ggplot(aes(lon, lat, color = avg_delay)) +
    borders("state") +
    geom_point() +
    coord_quickmap()
```

2. Add the location of the origin and destination (i.e. the lat and lon) to 
flights.
```{r}
flights %>%
  left_join(airports, c("dest" = "faa")) %>%
  left_join(airports, c("origin" = "faa")) %>%
  summarise(origin, name.y, lat.y, lon.y, dest, name.x, lat.x, lon.x)

```

3. Is there a relationship between the age of a plane and its delays?
```{r, warning = FALSE}
flights %>%
  left_join(planes, by="tailnum") %>%
  mutate(age = year.x - year.y) %>%
  group_by(age) %>%
  summarise(avg_delay = mean(arr_delay, na.rm = T)) %>%
  ggplot(aes(age, avg_delay)) + geom_point()
```

There seems to be no relationship between the age of a plane and its delays 
because the points are spread out across all ages groups. 